---
author: "Eugene Joh"
date: "`r format(Sys.Date(), '%A, %B %d, %Y')`"
output: 
  html_document:
    code_folding: hide
    theme: simplex
    highlight: tango
    df_print: kable
    css: toc_css.css
    toc: yes
    toc_depth: 3
params:
  set_title: "Data Profile: blank" #Title "EDA: ..." followed by dataframe name
  len_i: 1 #number of data frames in list `length(my_list)`
  dat: list[i] #actual list `my_list`
  name_i: "first list object" #name of each list `names(my_list)`
  cont: TRUE #logical to include continuous variables
  cat: TRUE #logical to include categorical variables
title: "`r params$set_title`"
---

<!-- The input for this parameterized R markdown file is a named `list` of `data.frames` -->
<!-- The parameters above specify the title used (dependent on each named object in `list`), number of `data.frames` in the list, names of the `data.frames`, logical for whether you want to include continuous and/or categorical variables. -->

```{r setup, include=FALSE}
bt <- proc.time()
if (!require(here)) install.packages("here")
# setup knitr chunks
knitr::opts_chunk$set(echo = TRUE, fig.width = 9.2, message = FALSE, warning = FALSE)

# load functions from "R" folder
if (any(grepl("R", list.files(here::here())))) invisible(lapply(list.files(here::here("R"), full.names = TRUE), source))

# scale for fig height
nvar <- length(names(params$dat))
fig.h <- nvar*0.8
```

```{r load_packages, echo=FALSE, include=FALSE}
packs <- c("haven","dplyr","tidyr","purrr","data.table","forcats","stringr", #process
           "ggplot2","scales","ggfortify","grid","gridExtra", #data viz
           "kableExtra","DT","htmlwidgets") #html widgets
install_packs(packs); rm(packs)
```

```{r first_test, include=FALSE, eval=TRUE}
cont_log <- params$cont
cat_log <- params$cat
```

# Overview 
This parameterized markdown file is a standarized exploratory analysis report, examining the data type, structure, missing values, unique values, summary statistics for continuous and categorical variables contained within a `data.frame` object.   

This does not support `date-time` varaibles such as `POSIXct` or `Date`, but will eventually move to support all data types typically found in `data.frame` in the R environment.  

# Data Structure
The input file **`r params$name_i`** is a `r class(params$dat)`. It contains `r nrow(params$dat)` rows and `r ncol(params$dat)` columns. The table below summarizes the data structure of the object. The column names are displayed in the code chunk below.  

```{r dims_tab, echo = FALSE}
data.frame(Object = paste0(params$name_i),
           ncol = ncol(params$dat),
           nrow = nrow(params$dat)) %>% 
  mutate(elements = ncol*nrow, size = paste0(format(object.size(params$dat), units = "auto"))) %>%
  add_kable(caption = "Dataset Dimensions", col.names = c("Name", "Number of Columns", "Number of Rows", "Number of Elements", "Memory Allocation"), format.args = list(decimal.mark =',', big.mark = "'"))
```

```{r colnames, echo = FALSE}
map_df(params$dat, class) %>% 
  gather(key = "Variable", value = "Class") %>% 
  mutate(missing = map_dbl(params$dat, ~sum(is.na(.)))) %>% 
  add_kable(caption = "Dataset Variable Class and Missing Values")
```

# Missing Values, Data Type, Unique Values

## Table
The table below displays the data type, counts/proportion of missing values `NA`, and whether the data is labelled or not.  
```{r na_type_tab, echo = FALSE}
tab_describe <- df_describe(params$dat)
tab_describe %>% 
  add_DT(caption = paste0("NA and Type Table ", params$name_i),
         colnames = c("Variable", "Missing (n)", "Missing (%)", "Exist (%)", "Data Type", "Labelled"))
```

## Plot
```{r plot_tab, fig.height = fig.h, echo = FALSE}
df_describe_p(tab_describe, params$dat, dat_name = params$name_i)
```

## Unique Values
```{r unique_tab, echo = FALSE}
length_unique(params$dat, kable = FALSE) %>% 
  add_DT(caption = paste0("Unique Values ", params$name_i))
```

# Variable Content {.tabset}
This section contains an analysis of the variable content composition by describing the type of data content that exist based on **numeric** values, **character** values, **punctuation** or **symbols**, and **blank** space. This is especially useful when data types are not identified or misclassified.  

## Only Numbers
**only_numbs** reports the number of rows that contain only digits `"^[0-9]{1,}$"` and **numpercent** is the respective percentage. **digits_min** and **digits_max** display the length of the digits found in the variable, **digits_eq** is a logical statment of whether the mix and max are equal.  
```{r nums, echo=FALSE}
.check_numbs_only(params$dat) %>% 
    left_join(.check_digit_length(params$dat), by = c("variable")) %>% 
  add_DT(caption = paste0("Only Numbers: ", params$name_i))
```

## Only Character
**only_char** reports the number of rows that contain only characters `"^[A-z]{1,}"` and **charpercent** is the respective percentage.  
```{r char, echo=FALSE}
.check_char_only(params$dat) %>% 
  add_DT(caption = paste0("Only Character: ", params$name_i))
```

## Only Punctuation
**only_punc** reports the number of rows that contain only punctuation or symbols `"^\\W+$"` and **puncpercentage** is the respective percentage.   
```{r punct, echo=FALSE}
.check_punc_only(params$dat) %>% 
  add_DT(caption = paste0("Only Punctuation: ", params$name_i))
```

## Only Blanks
**only_blanks** reports the number of rows that contain a blank ("") `"^\\s{0}$"` and **blankspercent** is the respective percentage. **only_wspace** reports the number of rows that contain any white-space, including a blank `"^\\s*$"` and **wspacepercent** is the respective percentage.  
```{r blank, echo=FALSE}
.check_blanks_only(params$dat) %>% 
  left_join(.check_wspace_only(params$dat), by = c("variable")) %>% 
  select(-n_row.x, -n_row.y) %>% 
    add_DT(caption = paste0("Only Blanks: ", params$name_i))
```

## All Types
```{r chr_num_tab, echo=FALSE}
tab_check <- check_all(params$dat)
tab_check %>% 
  add_DT(caption = paste0("All Content Types for ", params$name_i))
```

# Variable Content Plot
```{r p_content, fig.height=fig.h, echo=FALSE}
tab_check %>% select(variable, only_numbs, only_char, only_punc, only_blanks) %>% 
  gather(key="var_name",value="num_rows",-variable) %>% 
  mutate(var_name = factor(var_name, 
                           levels = c("only_numbs", "only_char", "only_punc", "only_blanks"),
                           labels = c("Numbers", "Character", "Punctuation", "Blanks"))) %>% 
  ggplot(aes(x=forcats::fct_inorder(variable), y=num_rows, fill = var_name)) +
  geom_bar(stat='identity', colour = "grey15") +
  coord_flip() +
  scale_fill_brewer(type = "qual", palette = 6, name = "Content") +
  labs(title = paste0(params$name_i, ": Variable Content Composition"),
       x = "Variable", y = "Number of Rows")
```


<!-- Continuous Variables -->
```{r include = FALSE}
if (length(names(dplyr::select_if(params$dat, is.numeric))) < 1) {
  cont_log <- FALSE #set condition for creating following code chunks
}
```

`r if(cont_log) {"# Continuous Variables"}`
```{r cont_vars-md, include=FALSE, message=FALSE}
out_cont <- NULL
for (j in names(dplyr::select_if(params$dat, is.numeric))) { #based on the names that are numeric
  out_cont <- c(out_cont, knitr::knit_child('cont_var.Rmd')) #apply child .Rmd to select variables
}
```
`r paste(out_cont, collapse = '\n')`

<!-- Categorical Variables -->
```{r}
if (length(names(dplyr::select_if(params$dat, funs(is.character(.) | is.factor(.))))) == 0) {
  cat_log <- FALSE
}
```

`r if(cat_log) {"# Categorical Variables"}`
```{r catgorical_vars-md, include=FALSE}
out_cat <- NULL

for (k in names(dplyr::select_if(params$dat, funs(is.character(.) | is.factor(.))))) {
  out_cat <- c(out_cat, knitr::knit_child('cat_var.Rmd'))
}
```
`r paste(out_cat, collapse = '\n')`


# R Session Info
```{r echo = FALSE}
sessionInfo()
```

<br>
<br>
Process Time: `r round((proc.time()["elapsed"] - bt["elapsed"])/60, 1)` minutes  
`r version$version.string`  
Report by the [Centre for Global Health Research](www.cghr.org/)
