---
author: "Eugene Joh"
date: "`r format(Sys.Date(), '%A, %B %d, %Y')`"
output: 
  html_document:
    code_folding: hide
    theme: simplex
    highlight: tango
    df_print: kable
    css: toc_css.css
    toc: yes
    toc_depth: 3
params:
  set_title: "Data Profile: blank" #Title "EDA: ..." followed by dataframe name
  len_i: 1 #number of data frames in list `length(my_list)`
  dat: list[i] #actual list `my_list`
  name_i: "first list object" #name of each list `names(my_list)`
  cont: TRUE #logical to include continuous variables
  cat: TRUE #logical to include categorical variables
title: "`r params$set_title`"
---

<!-- The input for this parameterized R markdown file is a named `list` of `data.frames` -->
<!-- The parameters above specify the title used (dependent on each named object in `list`), number of `data.frames` in the list, names of the `data.frames`, logical for whether you want to include continuous and/or categorical variables. -->

```{r setup, include=FALSE}
bt <- proc.time()
if (!require(here)) install.packages("here")
# setup knitr chunks
knitr::opts_chunk$set(echo = TRUE, fig.width = 9.2, message = FALSE, warning = FALSE)

# load functions from "R" folder
if (any(grepl("R", list.files(here::here())))) invisible(lapply(list.files(here::here("R"), full.names = TRUE), source))
```

```{r load_packages, echo=FALSE, include=FALSE}
packs <- c("dplyr","tidyr","purrr","data.table","forcats","stringr", #process
           "ggplot2","scales","ggfortify","grid","gridExtra", #data viz
           "kableExtra","DT","htmlwidgets") #html widgets
install_packs(packs); rm(packs)
```

```{r first_test, include=FALSE, eval=FALSE}
cont_log <- TRUE
cat_log <- TRUE
```

# Overview 
This parameterized markdown file is a standarized exploratory analysis report, examining the data type, structure, missing values, unique values, summary statistics for continuous and categorical variables contained within a `data.frame` object.   

This does not support `date-time` varaibles such as `POSIXct` or `Date`, but will eventually move to support all data types typically found in `data.frame` in the R environment.  

# Data Structure
The input file **`r params$name_i`** is a `r class(params$dat)`. It contains `r nrow(params$dat)` rows and `r ncol(params$dat)` columns. The table below summarizes the data structure of the object. The column names are displayed in the code chunk below.  

```{r dims_tab, echo = FALSE}
data.frame(Object = paste0(params$name_i),
           ncol = ncol(params$dat),
           nrow = nrow(params$dat)) %>% 
  mutate(elements = ncol*nrow, size = paste0(format(object.size(params$dat), units = "auto"))) %>%
  add_kable(caption = "Dataset Dimensions", col.names = c("Name", "Number of Columns", "Number of Rows", "Number of Elements", "Object Size"), format.args = list(decimal.mark =',', big.mark = "'"))
```

```{r colnames, echo = FALSE}
map_df(params$dat, class) %>% 
  gather(key = "Variable", value = "Class") %>% 
  mutate(missing = map_dbl(params$dat, ~sum(is.na(.)))) %>% 
  add_kable(caption = "Dataset Variable Class and Missing Values")
```

<!-- Continuous Variables -->
```{r include = FALSE}
if (length(names(dplyr::select_if(params$dat, is.numeric))) < 1) {
  cont_log <- FALSE #set condition for creating following code chunks
}
```

`r if(cont_log) {"# Continuous Variables {.tabset}"}`
```{r cont_vars-md, include=FALSE, message=FALSE}
out_cont <- NULL
for (j in names(select_if(params$dat, is.numeric))) { #based on the names that are numeric
  out_cont <- c(out_cont, knitr::knit_child('cont_var.Rmd')) #apply child .Rmd to select variables
}
```
`r paste(out_cont, collapse = '\n')`

<!-- Categorical Variables -->
```{r}
if (length(names(select_if(params$dat, funs(is.character(.) | is.factor(.))))) == 0) {
  cat_log <- FALSE
}
```

`r if(cat_log) {"# Categorical Variables {.tabset}"}`
```{r catgorical_vars-md, include=FALSE}
out_cat <- NULL

for (k in names(select_if(params$dat, funs(is.character(.) | is.factor(.))))) {
  out_cat <- c(out_cat, knitr::knit_child('cat_var.Rmd'))
}
```
`r paste(out_cat, collapse = '\n')`


# R Session Info
```{r echo = FALSE}
sessionInfo()
```

<br>
<br>

Report by the [Centre for Global Health Research](www.cghr.org/)
